Spatial Analysis

### 2021-10-29 Scripts/spatial_analisis.Rmd
misc.
updated webpage with new ports

---
title: "Spatial Analysis"
author: "Juliano Palacios Abrantes"
output:
  html_document:
  # html_notebook:
    fig_width: 6
    fig_height: 4
    code_folding: hide
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
    theme: darkly
---

@@

# Save data for future analysis
# write_csv(noaa_ports_complete,
#           my_path("D","NOAA", name = "top_ports.csv")
#           )

@@

@@

ggplot() +
  geom_sf(data = eez_sf, aes(),fill = NA) +
  geom_sf(data = port_bf, aes(color = species_name), fill = NA) +
  scale_color_manual(values = state_pallet)+
  theme_dark()

@@

# write_csv(inter_grid_df, paste0(my_path("D", "Spatial"),"inter_grid_df.csv"))

@@

# ---------------- #
# Convert grid to sf 
# ---------------- #
grid_fp_sf <- st_as_sf(ne_grid,
             coords = c("lon", "lat"),
             crs = 4326) %>% 
  st_join(port_bf) %>% # join to port sf
  filter(!is.na(landing_port)) %>%
  distinct(index,landing_port, .keep_all = TRUE) #removes like 400K overlapping rows

# Create data frame for future computations
# Note, will be used in next chunk
grid_fp_bf_dt <- as.data.frame(grid_fp_sf) %>%
    select(index,landing_port,species_name)

@@

gridExtra::grid.arrange(
  # Overall (overlapping) position
  ggplot(grid_fp_sf) +
    geom_sf(data = port_sf, aes(), fill = NA) +
    geom_sf(aes(color = state), alpha = 0.3) +
    geom_sf(data = eez_sf, aes(),fill =NA) + 
    scale_color_manual(values = state_pallet) +
    theme_dark() +
    theme(legend.position = ""),
  # Showing each state separately
  ggplot() +
    geom_sf(data = grid_fp_sf, aes(color = state),size = 0.1, alpha = 0.5) +
    facet_wrap(~state) +
    theme_dark() +
    theme(legend.position = "top") +
    scale_color_manual(values = state_pallet),
  nrow = 1)

@@

write_sf(grid_eez_sf_fp, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp.shp"))

# Get final df with index
grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
  select(index,landing_port,abrev=landing_state,spp=species_name) %>% 
  left_join(ne_grid,
            by = "index") %>% 
  left_join(state_names)

write_csv(grid_eez_fp_df, paste0(my_path("D", "Spatial/grid_eez_fp_sf"),"grid_eez_fp_df.csv"))

# Plot to make sure makes sense
grid_eez_sf_fp %>%
  ggplot() +
  geom_sf(aes(color = state), alpha = 0.3) +
  scale_color_manual(values = state_pallet) +
  geom_sf(data = eez_sf,aes(), fill = NA) +
  theme_dark()

@@

@@

@@

![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_agg_sptl.jpg)

@@

```
![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp_sptl.jpg)

@@

@@

![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/temp_proportion_chng.jpg)

@@

![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_agg.jpg)
```{r sarah_landings_data}

>>>>

---
title: "Spatial Analysis"
author: "Juliano Palacios Abrantes"
output:
  # html_document:
  html_notebook:
    fig_width: 6
    fig_height: 4
    code_folding: hide
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
    theme: darkly
---

@@

# Save data for future analysis
# write_csv(noaa_ports_complete,
#           my_path("D","Partial", name = "top_ports.csv")
#           )

@@

#Load top port data 
ports_df <- my_path("D","Partial", "top_ports.csv", read = T) %>% 
  filter(tresh == "75th") %>%
  distinct(port_name, .keep_all = T) # No need for duplication

@@

ggplot() +
  geom_sf(data = eez_sf, aes(),fill = NA) +
  geom_sf(data = port_bf, aes(), fill = NA) +
  scale_color_manual(values = state_pallet)+
  theme_dark()

@@

# Save grid for future analysis
# write_csv(inter_grid_df, paste0(my_path("R", "Partial"),"inter_grid_df.csv"))

@@

# ---------------- #
# Convert grid to sf 
# ---------------- #
grid_fp_sf <- st_as_sf(ne_grid,
             coords = c("lon", "lat"),
             crs = 4326) %>% 
  st_join(port_bf) %>% # join to port sf
  filter(!is.na(port_name)) %>%
  distinct(index,port_name, .keep_all = TRUE) #removes like 400K overlapping rows

# Create data frame for future computations
# Note, will be used in next chunk
grid_fp_bf_dt <- as.data.frame(grid_fp_sf) %>%
    select(index,port_name,species_name)

@@

gridExtra::grid.arrange(
  # Overall (overlapping) position
  ggplot(grid_fp_sf) +
    geom_sf(data = port_sf, aes(), fill = NA) +
    geom_sf(aes(color = state_postal), alpha = 0.3) +
    geom_sf(data = eez_sf, aes(),fill =NA) + 
    scale_color_manual(values = state_pallet) +
    theme_dark() +
    theme(legend.position = ""),
  # Showing each state separately
  ggplot() +
    geom_sf(data = grid_fp_sf, aes(color = state_postal),size = 0.1, alpha = 0.5) +
    facet_wrap(~state_postal) +
    theme_dark() +
    theme(legend.position = "top") +
    scale_color_manual(values = state_pallet),
  nrow = 1)

@@

write_sf(grid_eez_sf_fp, my_path("R", "Partial",name="grid_eez_fp.shp"))

# Get final df with index
grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
  select(index,port_name,abrev=state_postal,spp=species_name) %>% 
  left_join(ne_grid,
            by = "index")

write_csv(grid_eez_fp_df, my_path("R", "Partial/grid_fp",name = "grid_eez_fp_df.csv"))

# Plot to make sure makes sense
grid_eez_sf_fp %>%
  ggplot() +
  geom_sf(aes(color = state_postal), alpha = 0.3) +
  scale_color_manual(values = state_pallet) +
  geom_sf(data = eez_sf,aes(), fill = NA) +
  theme_dark()

@@

```{r data_prep, eval = F, echo = T, results='hide'}

@@

```{r sea_unit_map_diff, eval = F, echo = T, results='hide'}

@@

@@

```
<!-- ![Proportion change aggregated all species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/area_plot_avg_spp_sptl.jpg) -->

@@

```{r eval = F, echo = T, results='hide'}

@@

@@
